Federated Imputation

### 2020-06-28 federated_imp_synthesizing_complete_data.Rmd

@@

```{r, include = F}
source("2.a Synthesize data (m=1).R")
```

```{r, echo = F}
knitr::kable(syn1_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing approaches (complete data, same subset 1000 times, 1000 different subsets, all with the number of synthetic datasets equal to 1.")
```

@@

```{r, include = F}
source("2.b Synthesize data (m=5).R")
```

```{r, echo = F}
knitr::kable(syn5_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv based on synthesizing the data as a whole, based on 5 synthetic datasets per iteration.")
```

@@

```{r, include = F}
source("2.c Synthesize data mvnorm.R")
```

## Synthesizing by a linear regression model

```{r, echo = F}
knitr::kable(synth_by_lm, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
```

## Synthesizing by a Classification and Regression Tree (CART)

```{r}
knitr::kable(synth_by_cart, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
```

@@

```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
source("2.a Synthesize data (m=1).R")
```

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
knitr::kable(syn1_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing approaches (complete data, same subset 1000 times, 1000 different subsets, all with the number of synthetic datasets equal to 1.")
```

@@

```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
source("2.b Synthesize data (m=5).R")
```

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
knitr::kable(syn5_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv based on synthesizing the data as a whole, based on 5 synthetic datasets per iteration.")
```

@@

```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
source("2.c Synthesize data mvnorm.R")
```

## Inference with sample variance estimates

Sample variance estimates are computed as $V_{\bar{\hat{\beta}}} = \frac{1}{m} \sum_{i=1}^m V_{\hat{\beta}_i}$. However, confidence interval coverage is computed with respect to the true population value, instead of the sample estimates.

### Synthesizing by a linear regression model

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
knitr::kable(synth_by_lm, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
```

### Synthesizing by a Classification and Regression Tree (CART)

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
knitr::kable(synth_by_cart, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
```

## Inference with sample variance estimates

Population variance estimates are computed as <!-- TO DO - ADD CORRECT FORMULA $V_{\bar{\hat{\beta}}} = \frac{1}{m} \sum_{i=1}^m V_{\hat{\beta}_i}$ -->. However, confidence interval coverage is computed with respect to the true population value, instead of the sample estimates.

### Synthesizing by a linear regression model

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
knitr::kable(synth_by_lm_pop, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
```

### Synthesizing by a Classification and Regression Tree (CART)

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
knitr::kable(synth_by_cart_pop, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
```

### Variance estimates

The variance of the statistic of interest equals $\bar{v}_M$, which represents the average variance over the $M$ synthetic datasets, when the goal of the synthesis is to make inferences with regard to the sample at hand, instead of with regard to the population. When the goal of the synthesis is to make population inferences, the variance is adjusted with an additional term, based on the number of synthetic datasets: 
$$
Var(Q) = \bar{\mathcal{v}}_M (1 + \frac{1}{M})
$$
where $Q$ is the regression coefficient of the $k^{th}$ variable, $\bar{v}_M$ is the mean of the variables over the $M$ syntheses. If the number of synthesized data points ($J$) is unequal to the number of observations in the dataset ($N$), a correction equal to $\frac{J}{N}$ is multiplied with $\bar{v}_M$.
